\large{\bf Large effects and the infinitesimal model }

### 2023-07-05 writeup.tex
stable sim

A substantial challenge for the field is to develop tractable models of trait evolution
that include contributions of both ``large'' and ``small'' effect loci.
In practice, breeders already embellish the ``animal model'' (essentially, the infinitesimal model)
to predict traits
by combining both effects of known large effect loci
and calculations using a relatedness matrix.  \comment{cite}
We can study any model with simulation,
but the way forwards to theoretical understanding seems murky.

@@

\subsection*{Acknowledgements}
Thanks go to Nate Pope for useful discussion
and to Gregor Gorjanc for references to the literature.

>>>>

A substantial challenge for the field is to develop tractable models of trait evolution
that include contributions of both ``large'' and ``small'' effect loci.
In practice, breeders have long embellished the ``animal model'' (essentially, the infinitesimal model)
to predict traits
by combining both effects of known large effect loci
and calculations using a relatedness matrix
\citep[e.g.,][]{fernando1989marker,teissier2018weighted,bernardo2014genomewide,rice2019evaluation}.
We can study any model with simulation,
but the way forwards to theoretical understanding seems murky.

@@

\subsection*{Acknowledgements}
Thanks go to Nate Pope for useful discussion
and to Gregor Gorjanc for insight into modern uses
of the animal model and genomic selection.
